### 2020-03-05 2020.csic5011/homework/homework02.tex
Add files via upload

\item {\em Exploring S$\&$P500 Stock Prices:} Take the Standard \& Poor's 500 data: \\
%\url{http://math.stanford.edu/~yuany/course/data/snp452-data.mat},\\
\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/snp452-data.mat} \\ 
which contains the data matrix $X\in \R^{n\times p}$ of $n=1258$ consecutive observation days and $p=452$ daily closing stock prices, and the cell variable ``${\rm stock}$" collects the names, codes, and the affiliated industrial sectors of the 452 stocks. Use Matlab, Python, or R for the following exploration. 
\begin{enumerate}
\item Take the logarithmic prices $Y=\log X$; 
\item For each observation time $t\in \{1,\ldots,1257\}$, calculate logarithmic price jumps
\[ \Delta Y_{i,t} = Y_{i,t} - Y_{i,{t-1}}, \ \ \ i\in \{ 1,\ldots, 452 \}; \]
\item Construct the realized covariance matrix $\hat{\Sigma}\in\R^{452\times 452}$ by,
\[ \hat{\Sigma}_{i,j} = \frac{1}{1257} \sum_{\tau =1}^{1257} \Delta Y_{i,\tau} \Delta Y_{j, \tau}; \]
\item Compute the eigenvalues (and eigenvectors) of $\hat{\Sigma}$ and store them in a descending order by $\{\hat{\lambda}_k, k=1,\ldots,p\}$. 
\item \emph{Horn's Parallel Analysis}: the following procedure describes a so-called Parallel Analysis of PCA using random permutations on data. Given the matrix $[\Delta Y_{i,t}]$, apply random permutations $\pi_i: \{1,\ldots,t\} \to \{1,\ldots, t\}$ on each of its rows: $\Delta \tilde{Y}_{i,\pi_i(j)}$ such that 
\[
[\Delta \tilde{Y}_{\pi(i),t}] = \left[
\begin{array}{ccccc}
\Delta Y_{1,1} & \Delta Y_{1,2} & \Delta Y_{1,3} & \ldots & \Delta Y_{1,t} \\
\Delta Y_{2,\pi_2(1)} & \Delta Y_{2,\pi_2(2)} & \Delta Y_{2,\pi_2(3)} & \ldots & \Delta Y_{2,\pi_2(t)} \\
\Delta Y_{3,\pi_3(1)} & \Delta Y_{3,\pi_3(2)} & \Delta Y_{3,\pi_3(3)} & \ldots & \Delta Y_{3,\pi_3(t)} \\
\ldots & \ldots & \ldots & \ldots & \ldots \\
\Delta Y_{n,\pi_n(1)} & \Delta Y_{n,\pi_n(2)} & \Delta Y_{n,\pi_n(3)} & \ldots & \Delta Y_{n,\pi_n(t)} 
\end{array}
\right].
\]
Define $\tilde{\Sigma} = \frac{1}{t} \Delta \tilde{Y} \cdot \Delta \tilde{Y}^T$ as the null covariance matrix. Repeat this for $R$ times and compute the eigenvalues of $\tilde{\Sigma}_r$ for each $1\leq r\leq R$. Evaluate the $p$-value for each estimated eigenvalue $\hat{\lambda}_k$ by $(N_k + 1)/(R+1)$ where $N_k$ is the counts that $\hat{\lambda}_k$ is less than the $k$-th largest eigenvalue of $\tilde{\Sigma}_r$ over $1\leq r \leq R$. Eigenvalues with small $p$-values indicate that they are less likely arising from the spectrum of a randomly permuted matrix and thus considered to be signal. Draw your own conclusion with your observations and analysis on this data. A reference is: Buja and Eyuboglu, "Remarks on Parallel Analysis", Multivariate Behavioral Research, 27(4): 509-540, 1992.
\end{enumerate}

>>>>

\item {\em Exploring S$\&$P500 Stock Prices:} Take the Standard \& Poor's 500 data: \\
%\url{http://math.stanford.edu/~yuany/course/data/snp452-data.mat},\\
\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/snp452-data.mat} \\ 
which contains the data matrix $X\in \R^{p\times n}$ of $n=1258$ consecutive observation days and $p=452$ daily closing stock prices, and the cell variable ``${\rm stock}$" collects the names, codes, and the affiliated industrial sectors of the 452 stocks. Use Matlab, Python, or R for the following exploration. 
\begin{enumerate}
\item Take the logarithmic prices $Y=\log X$; 
\item For each observation time $t\in \{1,\ldots,1257\}$, calculate logarithmic price jumps
\[ \Delta Y_{i,t} = Y_{i,t} - Y_{i,{t-1}}, \ \ \ i\in \{ 1,\ldots, 452 \}; \]
\item Construct the realized covariance matrix $\hat{\Sigma}\in\R^{452\times 452}$ by,
\[ \hat{\Sigma}_{i,j} = \frac{1}{1257} \sum_{\tau =1}^{1257} \Delta Y_{i,\tau} \Delta Y_{j, \tau}; \]
\item Compute the eigenvalues (and eigenvectors) of $\hat{\Sigma}$ and store them in a descending order by $\{\hat{\lambda}_k, k=1,\ldots,p\}$. 
\item \emph{Horn's Parallel Analysis}: the following procedure describes a so-called Parallel Analysis of PCA using random permutations on data. Given the matrix $[\Delta Y_{i,t}]$, apply random permutations $\pi_i: \{1,\ldots,t\} \to \{1,\ldots, t\}$ on each of its rows: $\Delta \tilde{Y}_{i,\pi_i(j)}$ such that 
\[
[\Delta \tilde{Y}_{\pi(i),t}] = \left[
\begin{array}{ccccc}
\Delta Y_{1,1} & \Delta Y_{1,2} & \Delta Y_{1,3} & \ldots & \Delta Y_{1,t} \\
\Delta Y_{2,\pi_2(1)} & \Delta Y_{2,\pi_2(2)} & \Delta Y_{2,\pi_2(3)} & \ldots & \Delta Y_{2,\pi_2(t)} \\
\Delta Y_{3,\pi_3(1)} & \Delta Y_{3,\pi_3(2)} & \Delta Y_{3,\pi_3(3)} & \ldots & \Delta Y_{3,\pi_3(t)} \\
\ldots & \ldots & \ldots & \ldots & \ldots \\
\Delta Y_{n,\pi_n(1)} & \Delta Y_{n,\pi_n(2)} & \Delta Y_{n,\pi_n(3)} & \ldots & \Delta Y_{n,\pi_n(t)} 
\end{array}
\right].
\]
Define $\tilde{\Sigma} = \frac{1}{t} \Delta \tilde{Y} \cdot \Delta \tilde{Y}^T$ as the null covariance matrix. Repeat this for $R$ times and compute the eigenvalues of $\tilde{\Sigma}_r$ for each $1\leq r\leq R$. Evaluate the $p$-value for each estimated eigenvalue $\hat{\lambda}_k$ by $(N_k + 1)/(R+1)$ where $N_k$ is the counts that $\hat{\lambda}_k$ is less than the $k$-th largest eigenvalue of $\tilde{\Sigma}_r$ over $1\leq r \leq R$. Eigenvalues with small $p$-values indicate that they are less likely arising from the spectrum of a randomly permuted matrix and thus considered to be signal. Draw your own conclusion with your observations and analysis on this data. A reference is: Buja and Eyuboglu, "Remarks on Parallel Analysis", Multivariate Behavioral Research, 27(4): 509-540, 1992.
\end{enumerate}
